Isabelle/C/Clean - A Show-Case for a Semantic Back-End for Isabelle/C

### 2019-10-30 C11-BackEnds/Clean/document/root.tex
Global Restructuring and Document Adaption

\title{Clean - An Abstract Imperative Programming Language and its Theory}
\author{%
  \href{https://www.lri.fr/~ftuong/}{Fr\'ed\'eric Tuong}
  \and
  \href{https://www.lri.fr/~wolff/}{Burkhart Wolff} \\
  \and
  (with Contributions of \href{https://www.lri.fr/~keller/}{Chantal Keller})}
\publishers{%
  \mbox{LRI, Univ. Paris-Sud, CNRS, Universit\'e Paris-Saclay} \\
  b\^at. 650 Ada Lovelace, 91405 Orsay, France \texorpdfstring{\\}{}
}

@@

\begin{abstract}
Clean is based on a simple, abstract execution model for an imperative target language. ``Abstract''
is understood as contrast to ``Concrete Semantics''; alternatively, the term ``shallow-style
embedding'' could be used. It strives for a type-safe notation of program-variables, an incremental
construction of the typed state-space, support of incremental verification, and 
open-world extensibility of new type definitions being intertwined with the program
definition.

@@

Clean's design strives for extreme simplicity. It is geared towards symbolic execution and proven
correct verification tools. The underlying libraries of this package, however, deliberately restrict
themselves to the most elementary infrastructure for these tasks. The package is intended to serve
as demonstrator semantic backend for Isabelle/C~\cite{TuongWolff19}, or for the test-generation
technique described in~\cite{DBLP:conf/tap/Keller18}.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \input{session}
\newpage
\input{Clean.tex}

\input{Quicksort_concept.tex}
\input{SquareRoot_concept.tex}

\newpage
\chapter{Appendix : Used Monad Libraries}
\input{MonadSE.tex}
\input{Seq_MonadSE.tex}
\input{Symbex_MonadSE.tex}
\input{Hoare_MonadSE.tex}
\input{Hoare_Clean.tex}

>>>>

\title{Clean - An Abstract Imperative Programming Language and its Theory}
\author{%
  \href{https://www.lri.fr/~ftuong/}{Fr\'ed\'eric Tuong}
  \and
  \href{https://www.lri.fr/~wolff/}{Burkhart Wolff} \\
  \and
  (with Contributions by \href{https://www.lri.fr/~keller/}{Chantal Keller})}
\publishers{%
  \mbox{LRI, Univ. Paris-Sud, CNRS, Universit\'e Paris-Saclay} \\
  b\^at. 650 Ada Lovelace, 91405 Orsay, France \texorpdfstring{\\}{}
}

@@

\begin{abstract}
Clean is based on a simple, abstract execution model for an imperative target language. ``Abstract''
is understood as contrast to ``Concrete Semantics''; alternatively, the term ``shallow-style
embedding'' could be used. It strives for a type-safe notation of program-variables, an incremental
construction of the typed state-space, support of incremental verification, and 
open-world extensibility of new type definitions being intertwined with the program
definitions.

@@

Clean's design strives for extreme simplicity. It is geared towards symbolic execution and proven
correct verification tools. The underlying libraries of this package, however, deliberately restrict
themselves to the most elementary infrastructure for these tasks. The package is intended to serve
as demonstrator semantic backend for Isabelle/C~\cite{TuongWolff19}, or for the test-generation
techniques described in~\cite{DBLP:conf/tap/Keller18}.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \input{session}
\newpage
\input{Clean.tex}
\input{Quicksort_concept.tex}
\input{SquareRoot_concept.tex}
\input{LinearSearch}

\newpage
\chapter{Appendix : Used Monad Libraries}
\input{MonadSE.tex}
\input{Seq_MonadSE.tex}
\input{Symbex_MonadSE.tex}
\input{Clean_Symbex.tex}
\input{Test_Clean.tex}
\input{Hoare_MonadSE.tex}
\input{Hoare_Clean.tex}

### 2019-10-30 C11-BackEnds/Clean_wrapper/document/root.tex
generates .pdf with restrictions.

\documentclass[fontsize=11pt,paper=a4,open=right,twoside,abstract=true]{scrreprt}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[numbers, sort&compress, sectionbib]{natbib}
\usepackage{isabelle,isabellesym}
\usepackage[only,bigsqcap]{stmaryrd}
\usepackage{ifthen}
\usepackage{wrapfig}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{lstisadof}
\IfFileExists{railsetup.sty}{\usepackage{railsetup}}{}

@@

\newenvironment{matharray}[1]{\[\begin{array}{#1}}{\end{array}\]} % from 'iman.sty'
\newcommand{\indexdef}[3]%
{\ifthenelse{\equal{}{#1}}{\index{#3 (#2)|bold}}{\index{#3 (#1\ #2)|bold}}} % from 'isar.sty'
\newcommand{\isactrlC}{{\bf C}}

@@

\begin{abstract}
Isabelle/C ~\cite{TuongWolff19} is a C11 ~front-end for Isabelle/PIDE providing 
generic support for C parsing, editing, and highlighting. Isabelle/C also provides 
a generic interface for semantic interpretations of the C11 programs and program
fragments. In particular, Isabelle/C also offers the generic framework
to define \emph{annotation commands} and \emph{C antiquotations} 
that can be custumized to a specific semantic back-end.

@@

The current session instantiates Isabelle/C with Clean and produces the 
Isabelle/C/Clean instance. It is conceived as a demonstrator for creating
other instances of Isabelle/C with other semantic backends such as AutoCorres
~\cite{DBLP:conf/pldi/GreenawayLAK14},
IMP2~\cite{DBLP:journals/afp/LammichW19} or Orca~\cite{bockenek:hal-02069705}.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \input{session}
\newpage

%\newpage
%\chapter{Appendix : Used Monad Libraries}
\input{Backend.tex}				
\input{Clean.tex}				
\input{Core.tex}				
\input{Generator_dynamic_sequential.tex}	
\input{Init.tex}				
\input{Isabelle_code_runtime.tex}
%\input{Isabelle_typedecl.tex}
%\input{Meta_C.tex}

>>>>

\documentclass[fontsize=11pt,paper=a4,open=right,twoside,abstract=true]{scrreprt}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[numbers, sort&compress, sectionbib]{natbib}
\usepackage{isabelle,isabellesym}
\usepackage[only,bigsqcap]{stmaryrd}
\usepackage{ifthen}
\usepackage{wrapfig}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{listings}
\IfFileExists{railsetup.sty}{\usepackage{railsetup}}{}

\newcommand\inputif[1]{\IfFileExists{./#1}{\input{#1}}{}}

@@

\newenvironment{matharray}[1]{\[\begin{array}{#1}}{\end{array}\]} % from 'iman.sty'
\newcommand{\indexdef}[3]%
{\ifthenelse{\equal{}{#1}}{\index{#3 (#2)|bold}}{\index{#3 (#1\ #2)|bold}}} % from 'isar.sty'
\newcommand{\isactrlC}{{\isacommand C}}
\newcommand{\isactrlMLPRIME}{{\isacommand MLPRIME}}

@@

\begin{abstract}
Isabelle/C~\cite{TuongWolff19} is a C front-end for Isabelle/PIDE providing
generic support for C parsing, editing, and highlighting. Isabelle/C also
provides a generic interface for semantic interpretations of C11 programs and
program fragments. In particular, Isabelle/C also offers the generic framework
to define \emph{annotation commands} and \emph{C antiquotations} that can be
custumized to a specific semantic back-end.

@@

The current session instantiates Isabelle/C with Clean and produces the
Isabelle/C/Clean instance. It is conceived as a demonstrator for creating other
instances of Isabelle/C with other semantic backends such as
AutoCorres~\cite{DBLP:conf/pldi/GreenawayLAK14},
IMP2~\cite{DBLP:journals/afp/LammichW19} or Orca~\cite{bockenek:hal-02069705}.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \input{session}
\newpage
\inputif{1/document/Init.tex}
%\inputif{1/document/Meta_C.tex}
\inputif{1/document/Core.tex}
%\inputif{1/document/Isabelle_code_runtime.tex}
%\inputif{1/document/Isabelle_typedecl.tex}
%\inputif{1/document/Generator_dynamic_sequential.tex}
\inputif{1/document/Backend.tex}

%\inputif{2/document/IsPrime_sqrt_outside.tex}
%\inputif{2/document/Clean_backend_old.tex}
\inputif{2/document/Prime.tex}
\inputif{2/document/Quicksort2.tex}
\inputif{2/document/Quicksort.tex}

%\newpage
%\chapter{Appendix}
